### 2016-06-23 paper/numerical_experiments.tex
more edits to 3D example

Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering    
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \label{fig:baseRef0}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/setup_5_3.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/setup_7_3.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/setup_3_3.png}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_0.png}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_1.png}
    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_2.png}
    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
  \label{fig:qoiStudy}
\end{figure}

@@

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/setup_3_10.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/setup_3_5.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/setup_3_3.png}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup2}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_0.png}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF2}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_1.png}
    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_2.png}
    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
    \label{subfig:obsMFlast2}
  \end{subfigure}
  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF2}-\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\subref{subfig:obsSetup2})) and varying observations (teal points in (\subref{subfig:obsSetup2})).}
  \label{fig:dataStudy}
\end{figure}

@@

Figure~\ref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node. 
%
\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
\centering
\begin{subfigure}[b]{\textwidth}
\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_LF.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_0$ ($0\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF01.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_1$ ($10\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
  \centering
  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF02.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_2$ ($20\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF06.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_6$ ($60\%$ HF)}
\end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to Figure~\ref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.

@@

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

@@

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions. The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}. We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{series3D/setup_arial_nolegend.pdf} \hfill
\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
\vspace{\baselineskip}
\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
\caption{Three views of the locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%
We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements. The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom. The cell P\'{e}clet is small enough to not require stabilization.

@@

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration. For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
MF01 & 16.7 & 577582  & -0.03831 & -0.05222 & 1110 \\
MF02 & 29.0 & 548904  & 0.00219  & -0.00272 & 1800 \\
MF03 & 42.3 & 547773  & 0.00032  & -0.00064 & 2220 \\
HF   & 100  & 547420  & 0        & 0        & 6210 \\
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations.}
\label{tab:ref3D}
\end{table}
%
Compared to the previous examples in Section~\ref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. This is likely due to the additional difference in the diffusive coefficient of the two models in this case. The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within $0.1\%$, but in about a third of the time. %what happens if you go on forever? (running)

>>>>

Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Lagrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[h]
\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering    
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \label{fig:baseRef0}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/setup_5_3.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/setup_7_3.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/setup_3_3.png}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_0.png}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_1.png}
    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_2.png}
    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
  \label{fig:qoiStudy}
\end{figure}

@@

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/setup_3_10.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/setup_3_5.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/setup_3_3.png}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup2}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_0.png}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF2}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_1.png}
    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_2.png}
    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
    \label{subfig:obsMFlast2}
  \end{subfigure}
  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF2}-\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\subref{subfig:obsSetup2})) and varying observations (teal points in (\subref{subfig:obsSetup2})).}
  \label{fig:dataStudy}
\end{figure}

@@

Figure~\ref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node. 
%
\begin{figure}[h]
\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
\centering
\begin{subfigure}[b]{\textwidth}
\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_LF.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_0$ ($0\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF01.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_1$ ($10\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
  \centering
  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF02.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_2$ ($20\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.png}
  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF06.png}
  \vspace{-0.7\baselineskip}
  \caption{MF$_6$ ($60\%$ HF)}
\end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to Figure~\ref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.

@@

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_ru^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

@@

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions. The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}. We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{series3D/setup_aerial_nolegend.pdf} \hfill
\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
\vspace{\baselineskip}
\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
\caption{Three views of the locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%
We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements. The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom. The cell P\'{e}clet is small enough to not require stabilization.

@@

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration. For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
MF01 & 16.7 & 577582  & -0.03831 & -0.05222 & 1110 \\
MF02 & 29.0 & 548904  & 0.00219  & -0.00272 & 1800 \\
MF03 & 42.3 & 547773  & 0.00032  & -0.00064 & 2220 \\
HF   & 100  & 547420  & 0        & 0        & 6210 \\
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration.}
\label{tab:ref3D}
\end{table}
%
Compared to the previous examples in Section~\ref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. This is likely due to the additional difference in the diffusive coefficient of the two models in this case. The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within $0.1\%$, but in about a third of the time. %what happens if you go on forever? the sign corrects itself in the next two iterations, and then becomes wrong again...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs)...also 'continuation' this way is faster (4600) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...

The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}. We see that the error decomposition causes the first refinement iteration to target the QoI region and observations. Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\label{fig:ref3D_1}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D}
\end{figure} 
The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations. Refining a larger region per iteration runs the risks of refining in the wrong areas due to linearization about a $\Psi_{MF}$ that is very different from $\Psi_{HF}$, but can also allow one to reach the chosen error tolerance in fewer iterations and less runtime. We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement. Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
\begin{table}
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
MF01 & 9.27 & 613419  & -0.06649 & -0.10759 & 1040 \\
MF02 & 16.9 & 558523  & 0.00208  & -0.01988 & 1860 \\
MF03 & 23.7 & 550323  & 0.00456  & -0.00528 & 2420 \\
MF04 & 30.4 & 548225  & 0.00302  & -0.00147 & 2970 \\
